To be decided\\ Measuring Interaction before developing prototypes\\ Measuring Interaction Graphs

### 2015-09-09 paper.tex
initial draft of abstract and intro

\title{SIGCHI Conference Proceedings Format}

@@

\begin{abstract}
  UPDATED---\today. This sample paper describes the
  formatting requirements for SIGCHI conference proceedings, and
  offers recommendations on writing for the worldwide SIGCHI
  readership. Please review this document even if you have submitted
  to SIGCHI conferences before, as some format details have changed
  relative to previous years. Abstracts should be about 150 words and
  are required.
\end{abstract}

@@

Adopting Usage Centered Development practices is effective, as is
following established design principles~\cite{constantine99}. Early
prototyping~\cite{buxton07} and exploration of the 5-dimensional prototyping
space~\cite{mccurdy06} is one of the most effective techniques,
especially when paired with usability investigations based on user
testing or heuristic evaluations.

However, it requires development of prototypes that are usually
developed with certain tasks in mind, and therefore are quite
restricted in terms of depth and breadth of supported use
cases. Furthermore, usability results are always surrounded by a cloud
of uncertainty, due to subjectivity introduced by participants and
facilitators or by other contingency factors involved in the
analysis. Thus, although an effort needs to be expended to develop and
use prototypes, less than optimal results are obtained.

>>>>

\title{To be decided\\
Measuring Interaction before developing prototypes\\
Measuring Interaction Graphs}

@@

\begin{abstract}
  Early development of prototypes and testing them with users is a good
  practice for user interfaces development. However, prototypes have
  to cover specific usage scenarios, and because they are limited
  in focus, the whole picture of the user interface is easily lost. Even
  simple questions dealing with numerosity and length of
  optimal execution paths or impact of possible user errors can be
  answered only for the specific scenarios being analyzed.

  We discuss a tool that transforms models of the behavior of a user
  interface into a graph. This is then used to specify usage
  scenarios, and to generate possible execution traces. Metrics based
  on number and length of different possible execution paths, with or
  without possible mistakes, can be easily computed. We apply the tool
  and metrics to well known examples of web mail apps, and show that
  important conclusions can be drawn even before the first prototype
  is built.

\end{abstract}

@@

Adopting Usage Centered Development practices is effective, as is
following established design principles~\cite{constantine99}. Early
prototyping~\cite{buxton07} to explore part of the 5-dimensional
prototyping space~\cite{mccurdy06} is one of the most effective
techniques, especially when paired with usability investigations based
on user testing or heuristic evaluations.

However, it still requires development of prototypes that are usually
developed with certain tasks in mind, and therefore are quite
restricted in terms of depth and breadth of supported use
cases. Furthermore, usability results are always surrounded by a cloud
of uncertainty, due to subjectivity introduced by participants and
facilitators or by other contingency factors involved in the
analysis. Thus, although an effort needs to be expended to develop and
use prototypes, less than optimal results are obtained.
